Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-06 paper.tex
recompiled document

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

@@

\usepackage{caption}
\usepackage{subcaption}

@@

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{fit,bayesnet}
%\usetikzlibrary{arrows.meta}
%\usetikzlibrary{positioning}
%\usetikzlibrary{decorations.text}
%\usetikzlibrary{decorations.pathmorphing}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
\DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays

@@

Automatically inducing programs from examples is a long-standing goal
of artificial intelligence.  Recent work in program induction show
that deep networks can be very successful at learning to write certain
kinds of programs (e.g., RobustFill:~\cite{devlin2017robustfill} and
DeepCoder:~\cite{balog2016deepcoder}), as can symbolic search
techniques (e.g., Metagol:~\cite{muggleton2015meta} and 
FlashFill:~\cite{gulwani2011automating}).
However, the success of these approaches -- both symbolic and neural --
relies crucially upon a hand-engineered \emph{Domain Specific Language} (DSL).
The DSL is an inventory of restricted programming primitives,
that imparts domain specific knowledge about the space of programs.
To what extent can we dispense with hand-engineered DSLs?

>>>>

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

@@

\usepackage{caption}
%\usepackage{subcaption}

@@

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{fit,bayesnet}
%\usetikzlibrary{arrows.meta}
%\usetikzlibrary{positioning}
%\usetikzlibrary{decorations.text}
%\usetikzlibrary{decorations.pathmorphing}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays

@@

Automatically inducing programs from examples is a long-standing goal
of artificial intelligence.  Recent work in program induction show
that deep networks can be very successful at learning to write certain
kinds of programs (e.g., RobustFill:~\cite{devlin2017robustfill} and
DeepCoder:~\cite{balog2016deepcoder}), as can symbolic search
techniques (e.g., Metagol:~\cite{muggleton2015meta} and 
FlashFill:~\cite{gulwani2011automating}).
However, the success of these approaches -- both symbolic and neural --
relies crucially upon a hand-engineered \emph{Domain Specific Language} (DSL).
The DSL is an inventory of restricted programming primitives,
and imparts domain specific knowledge about the space of programs.
To what extent can we dispense with hand-engineered DSLs?
